Sparse Function-space Representation \\ of Neural Networks

### 2023-05-17 paper/main.tex
updfatedd
fixed typo

\paragraph{\our for dual conditioning} Adding new data to a trained neural network without retraining from scratch is a non-trivial problem. Some approaches exist \citep{kirsch2022marginal, spiegelhalter1990sequential} but are in the weight space formulation, which makes conditioning harder to formulate. As pointed out in \cite{chang2022fantasizing}, dual parameter conditioning updates are straightforward and were the original motivation of \cite{csato2002sparse}. This involves integrating data into the sum in \cref{eq:dual_sparse}. Thus, we need to find the data dual variables $\hat{\alpha}$ and $\hat{\beta}$ for the new data subset $\mathcal{D}_\textrm{new} = \{(\vx_i,\vy_i)\}_{i=1}^{N_{\textrm{new}}}$ and compute the corresponding kernel terms. As pointed out in \cite{chang2022fantasizing}, for GPs, these updates are exact under a Gaussian likelihood and the kernel remains constant. For non-Gaussian likelihoods, the results are almost the same as retraining with all the data. However, it is worth noting that our kernel's dependency on the trained neural network $\Jac{\weights_*}{\vx}$ (via the Jacobian) becomes outdated as we add more data. Nevertheless, we can still improve predictions by conditioning on new data without retraining.
%[SEE EXPERIMENT ???].
%%The resulting regularizer can be computed as follows
%%\begin{equation}
%%	\mathcal{R}_\textit{SFR}(\weights, \mathcal{M}) = \sum_{s=1}^{t-1} \frac{1}{m} \left[\left(f_{\weights}(\MZ_{s}) - f_{\weights_{s}}(\MZ_s) \right)^\T \bar{\MB}^{-1}_{s} \left(f_{\weights}(\MZ_{s}) - f_{\weights_{s}}(\MZ_s) \right) \right].
%%\end{equation}
%%
%\begin{equation}
%	\mathcal{R}_\mathrm{\our}(\weights, \mathcal{M}) = \frac{1}{2} \sum_{s=1}^{t-1} \frac{1}{M} 
%	\left\lVert 
%	f_{\weights}(\MZ_{s}) - \vu_t % f_{\weights_{s}}(\MZ_s)
%	\right\rVert_{\bar{\MB}^{-1}_{s}}.
%\end{equation}
%%\todo{choose one option}
%% where $f_\vw(\MZ_{s}) \in \R^m$ are the outputs of neural networks with the current weights $\vw$ and stored function outputs of the neural network at the MAP optimum for task $s$, i.e., each $i$th entry is $f_\cdot(\vz_i) \in \R$.
%%\begin{equation}
%%	\argmin_{\weights} \sum_{i=1}^{n} \ell(f_\weights(\mathbf{x}_{i}), \mathbf{y}_i) + \delta \mathcal{R}(\weights) + \tau \mathcal{R}_\textit{SFR}(\weights)
%%\end{equation}
%Then, when the training on the successive task, the new objective to minimize takes the following form
%\begin{equation}
%	\weights_t^* = \argmin_{\weights} \mathcal{L}(\mathcal{D}_t, \weights) + \tau \mathcal{R}_\textit{SFR}(\weights, \mathcal{M})
%\end{equation}

@@

\begin{table}[t!] 
  \centering\scriptsize
  \caption{Comparisons and ablations on UCI data with negative log predictive density (NLPD\textcolor{gray}{\footnotesize$\pm$std}, lower better). Our sparse \our ($M=256$) is on par with full models (left) and outperforms the GP subset approach of \cite{immer2021improving} (right). Results for methods marked with * as reported in teh original benchmark~\cite{immer2021improving}. See \cref{app:uci} for additional tables with comparisons.} 
	\label{tbl:uci}
	\vspace*{-4pt}

>>>>

\paragraph{\our for dual conditioning} Adding new data to a trained neural network without retraining from scratch is a non-trivial problem. Some approaches exist \citep{kirsch2022marginal, spiegelhalter1990sequential} but are in the weight space formulation, which makes conditioning harder to formulate. As pointed out in \cite{chang2022fantasizing}, dual parameter conditioning updates are straightforward and were the original motivation of \cite{csato2002sparse}. This involves integrating data into the sum in \cref{eq:dual_sparse}. Thus, we need to find the data dual variables $\hat{\alpha}$ and $\hat{\beta}$ for the new data subset $\mathcal{D}_\textrm{new} = \{(\vx_i,\vy_i)\}_{i=1}^{N_{\textrm{new}}}$ and compute the corresponding kernel terms. As pointed out in \cite{chang2022fantasizing}, for GPs, these updates are exact under a Gaussian likelihood and the kernel remains constant. For non-Gaussian likelihoods, the results are almost the same as retraining with all the data. However, it is worth noting that our kernel's dependency on the trained neural network $\Jac{\weights_*}{\vx}$ (via the Jacobian) becomes outdated as we add more data. Nevertheless, we can still improve predictions without retraining by conditioning on new data.
%[SEE EXPERIMENT ???].
%%The resulting regularizer can be computed as follows
%%\begin{equation}
%%	\mathcal{R}_\textit{SFR}(\weights, \mathcal{M}) = \sum_{s=1}^{t-1} \frac{1}{m} \left[\left(f_{\weights}(\MZ_{s}) - f_{\weights_{s}}(\MZ_s) \right)^\T \bar{\MB}^{-1}_{s} \left(f_{\weights}(\MZ_{s}) - f_{\weights_{s}}(\MZ_s) \right) \right].
%%\end{equation}
%%
%\begin{equation}
%	\mathcal{R}_\mathrm{\our}(\weights, \mathcal{M}) = \frac{1}{2} \sum_{s=1}^{t-1} \frac{1}{M} 
%	\left\lVert 
%	f_{\weights}(\MZ_{s}) - \vu_t % f_{\weights_{s}}(\MZ_s)
%	\right\rVert_{\bar{\MB}^{-1}_{s}}.
%\end{equation}
%%\todo{choose one option}
%% where $f_\vw(\MZ_{s}) \in \R^m$ are the outputs of neural networks with the current weights $\vw$ and stored function outputs of the neural network at the MAP optimum for task $s$, i.e., each $i$th entry is $f_\cdot(\vz_i) \in \R$.
%%\begin{equation}
%%	\argmin_{\weights} \sum_{i=1}^{n} \ell(f_\weights(\mathbf{x}_{i}), \mathbf{y}_i) + \delta \mathcal{R}(\weights) + \tau \mathcal{R}_\textit{SFR}(\weights)
%%\end{equation}
%Then, when the training on the successive task, the new objective to minimize takes the following form
%\begin{equation}
%	\weights_t^* = \argmin_{\weights} \mathcal{L}(\mathcal{D}_t, \weights) + \tau \mathcal{R}_\textit{SFR}(\weights, \mathcal{M})
%\end{equation}

@@

\begin{table}[t!] 
  \centering\scriptsize
  \caption{Comparisons and ablations on UCI data with negative log predictive density (NLPD\textcolor{gray}{\footnotesize$\pm$std}, lower better). Our sparse \our ($M=256$) is on par with full models (left) and outperforms the GP subset approach of \cite{immer2021improving} (right). Results for methods marked with * as reported in the original benchmark~\cite{immer2021improving}. See \cref{app:uci} for additional tables with comparisons.}
	\label{tbl:uci}
	\vspace*{-4pt}
